Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda

### 2013-04-29 Web3D2013-Dec3D/paper.tex
Polyfill section extended by Level of Integration

\subsection{Polyfill Approach}
\label{subsection:polyfill}

% http://www.w3.org/community/declarative3d/wiki/Level_of_Integration/
We also propose to measure a level of integration for 3D graphics in terms of W3C technologies (DOM, CSS, etc.) to explain existing and possible integration levels (Figure \ref{fig:polyInt} shows that currently only level 2, DOM integration, is possible here), and to finally identify a suitable integration level for declarative 3D. The latter imposes several problems in that it requires having a set of 3D-specific CSS properties or even a full shader description via CSS as well as a deeper integration into debugging tools like Chrome Developer Tools or Firebug. However, integration levels 3 and 4 are currently not yet achievable by a JavaScript implementation, because the required APIs are missing: it is not possible to introduce new CSS properties or to extend developer tools by an API.

It quickly became clear that a higher level of integration requires additional APIs in user agents. After discussions with browser vendors (namely Firefox and Chrome), who made it clear that integration of the desired extensions natively into their frameworks is not currently their priority, we decided to consider a so-called polyfill approach for the further development activities.
Nevertheless, communicating and requesting additional and missing features like custom CSS properties or CSS monitoring is necessary.

>>>>

\subsection{Level of Integration and Polyfill Approach}
\label{subsection:polyfill}

% http://www.w3.org/community/declarative3d/wiki/Level_of_Integration/
We also propose a measure for the Level of Integration~(LOI) for 3D graphics into the W3C technology stack (DOM, CSS, etc.) to explain existing and possible integration levels~(Figure \ref{fig:polyInt}). Level 0 is the classical integration using plug-ins. Many X3D implementations as well as Adobe's Flash and Unity 3D use the plug-in model to integrate their rendering engine into the browser. LOI 1 provides a dedicated element in the DOM in combination with an API. Currently  WebGL and the \verb|<canvas>| provide this level of integration. The next level (LOI 2) has the scene description not in JavaScript but integrated in the DOM. Levels 3 and 4 provide an even better integration with CSS and easy debugging of 3D scenes. This requires having a set of 3D-specific CSS properties or even a full shader description via CSS as well as a deeper integration into debugging tools like Chrome Developer Tools or Firebug.

Using existing APIs in the browser, we can emulate native Dec3D functionality up to level 2, with some initial support of existing CSS properties.
Integration levels 3 and 4 are currently not yet achievable by a JavaScript implementation, because the required APIs are missing: it is not possible to introduce new CSS properties or to extend developer tools by an API, a higher level of integration requires additional APIs in user agents. After discussions with browser vendors (namely Firefox and Chrome), who made it clear that integration of the desired extensions natively into their frameworks is not currently their priority, we decided to consider a so-called \textit{polyfill} approach for the further development activities.
Nevertheless, communicating and requesting additional and missing features like custom CSS properties or CSS monitoring is necessary.
